---
title: "scallop_markdown"
output: html_document
---

```{r, include=FALSE}
library(tidyr)
library(dplyr)
library(utils)
library(diveRsity)
library(ggplot2)
library(stargazer)
library(stats)
library(utils)
library(tinytex)
library(quantreg)
library(broom)
library(ggpubr)
library(rmarkdown)
```


```{r, include=FALSE}
scallop_df <- read.csv("../Data/Rdataformat_03132018.csv")
head(scallop_df)

df <- select(scallop_df, Location, FullScallop_Number, T1_height, T1_width,
                  T1_length, T2_height, T2_width, T2_length, T2_whole_weight, 
                  T2_body_weight, T2_adductor, sex, mc_1_mode, mc_2_mean, mc_3_max, sex)

```

**Linear Model**

This linear model allows us to determine important factors impacting adduction diameter of *Crassadomea gigantea*.

```{r, include=FALSE}
df$sex <- as.numeric(df$sex)
df$T2_length <- as.numeric(df$T2_length)
df$Location <- as.factor(df$Location)
df$T2_adductor <- as.numeric(df$T2_adductor)


linear_model <- lm(T2_adductor ~ sex+T2_length+T2_width+T2_height+mc_1_mode+Location, data = df)
summary(linear_model)
```

```{r, echo=FALSE}
# Table Output
stargazer(linear_model, title = "Linear Model",
          type= "text",
          out = "mini_project.html",
          covariate.labels=c( 'Sex', 'Length', 'Width', 'Height', 'Maturation Stage', 'Neah Bay', 'Totten Inlet'),
          dep.var.labels=c("Adductor Diameter (mm)", ""),
          single.row = T)
```

This table is showing that, given adductor diameter as the dependent variable, site and external metrics (length, width, height) are significant factors in predicting adductor diameter.

Thus we ran a linear regression with the external metric on the y axis and the adductor diameter and the x axis.
Correlation values for all three external metrics ranged from 0.5-0.6.

```{r, echo=FALSE, message=F, warning=F}
# External Metrics (T2) vs. Adductor Muscle Diameter

#T2_Length

plot1<- ggplot(df, aes(T2_length, T2_adductor)) +
  geom_jitter() +
  theme_classic()+
  xlab('Length (mm)')+
  ylab('Diameter (mm)')+
  ggtitle('Adductor Diameter vs. Shell Length')+
  geom_smooth(method='lm', aes(colour='black'))+
  theme(legend.position = 'none') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 20)) +
  scale_y_continuous(limits = c(0,20))+
  scale_x_continuous(limits = c(15,90))+
  annotate('text', label = "p-value = 1.863815e-37", x = 75, y = 1.5)



#T2_height

plot2<- ggplot(df, aes(T2_height, T2_adductor)) +
  geom_jitter() +
  theme_classic()+
  xlab('Height (mm)')+
  ylab('Diameter (mm)')+
  ggtitle('Adductor Diameter vs. Shell Height')+
  geom_smooth(method='lm', aes(colour='black'))+
  theme(legend.position = 'none') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 20))+
  annotate('text', label = 'p-value = 5.037393e-39', x = 75, y = 1.5)



#T2_width

plot3 <- ggplot(df, aes(T2_width, T2_adductor)) +
  geom_jitter() +
  theme_classic()+
  xlab('Width (mm)')+
  ylab('Diameter (mm)')+
  ggtitle('Adductor Diameter vs. Shell Width')+
  geom_smooth(method='lm', aes(colour='black'))+
  theme(legend.position = 'none') +
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = 'bold'))+
  annotate('text', label = 'p-value = 4.380831e-30', x = 20, y = 2)+
  xlim(8,25)



#build all the plots into one graph
multiplot(plot1,plot2,plot3,cols = 1)
```